Conjure: Summoning Proxies from Unused Address Space

### 2019-09-01 paper/paper.tex
Architecture updates for paper.

%\TODO{more precise:}
In our scheme (Figure~\ref{fig:highlevel}), clients
request the creation of phantom hosts in the ``dark''
or unused address space of the deploying ISP. Once registered, clients
can connect to these phantom hosts IP addresses as if they were real
proxy servers. The ISP station acts as the other end of these connections, and
responds as if it were a legitimate site or service. To the censor,
these phantom hosts appear as legitimate sites or services, and even
active probes will not reveal information that would allow the censor to
block them.

%% requests service
%% by embedding a steganographic registration message in a TLS handshake
%% with a decoy site. This message, which the ISP station can passively
%% observe using a private key, uniquely determines an IP address within
%% the ISP's address space. If there is no server running at that address,

@@

Phantom hosts are cheap to create, allowing for discardable or even one-time-use
proxy servers. This greatly increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
can detect 90\% of phantom hosts does not significantly increase the cost to the
circumvention system, giving \scheme an advantage in the censor/circumventor
cat-and-mouse game.
%TODO: don't need to hedge on IPv4 anymore..? couldcut
\scheme supports both IPv4 and IPv6,
though we note that the technique is especially
powerful in IPv6, where censors cannot exhaustively scan the address space
ahead of time to identify addresses that change behavior.
Because we fully control the transport connection, connections can live as
long as needed, without the complexity faced by TapDance.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented Conjure (Section~\ref{sec:implementation})
and deployed it on a 20~Gbps ISP testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}): on average, \scheme has 20\% lower latency,
14\% faster download bandwidth, and over 1400 times faster upload bandwidth.
In addition, \scheme provides significantly
more flexibility than existing Refraction protocols, allowing maintainers to
respond to future censor techniques.
We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

@@

\scheme involves two high-level steps. First, clients \textbf{register} with the
ISP station,
and agree on the phantom host IP address that will be used. Then, the client
connects to the agreed upon phantom address, which relays the client's traffic
to an \textbf{application}. If the application determines the traffic is from
the same client that originally registered (and not a probing censor), it
provides access to the proxy, tunneled through the application's protocol.

Similar to previous schemes, our design does not require expensive in-line
flow blocking, and can be accomplished with only a passive tap at the ISP.
Our architecture is also modular, in that the registration and application steps operate
independently, allowing a wide range of flexibility to evade censors. We
describe each of these components, and then describe our implementation and
deployment in Section~\ref{sec:implementation}.

\subsection{Registration}
\label{sec:registration}
Clients can register intent to use the proxy in several covert ways. For
instance, they could use email~\cite{SWEET-ToN} or any other existing intermittently
available proxies
to register. In this section, we use a form of Refraction Networking similar to
TapDance to register directly with the station, though note our scheme is simpler and more
difficult to detect or block compared to vanilla TapDance.
%We note this form is simpler and more difficult to detect or block than
%TapDance.

Registration is unidirectional (client to server) and does not require any
acknowledgement of receipt. To ensure receipt, clients can attempt to register
multiple times (possibly via multiple methods) with the same information, and expect
that one gets through.

@@

To register, clients connect to a \textbf{decoy} site that supports TLS. They
complete the handshake, and send a normal HTTPS request that embeds a special
steganographic \textbf{tag} in the ciphertext of the request. We use
the same technique used in TapDance's covert ciphertext
channel~\cite[\S3]{tapdance14}
to embed the tag, but we purposefully have the client
send a complete request (rather than incomplete), allowing the decoy server to respond.
The steganographic tag is only visible to the ISP station, which can see the tag using its
private key. Unlike in TapDance, the \scheme station can passively observe
the tag, and does not need to respond to it, obviating the need to mimick the decoy.
In addition, more potential decoys can be used than in TapDance, as
there is no need to exclude decoys that have timeouts or TCP windows unfavorable
for keeping connections open. In our ISP deployment, this results in a modest increase
of 25\% more decoys that could be used than in TapDance.

The tag contains a public key (encoded to be indistinguishable from random using
Elligator~\cite{elligator}), and a message encrypted under the shared secret
derived from a Diffie-Hellman key exchange with the station's long-term public key hard-coded
in the client software. The station uses its private key to compute the same
shared secret from the (decoded) client public key, and decrypts the message in the
tag. The censor, without knowledge of either the station or client's private
key, cannot derive the shared secret, preventing it from being able to decrypt
the message, or even learn of its existence.

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and a set of network prefixes that the client knows can be used
for phantom hosts (previously distributed publicly).
The client and server hash the seed to determine which specific
IP address from the set of prefixes will be used and registered as a phantom host.
It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected phantom hosts and block them if
they can be used as proxies.
By using a hash of a seed, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address.
It also gives a
secret (the seed) that only the client and station know, which can
later be used to verify a client connecting to the phantom host address is the
original registering client.
We discuss the intricacies of phantom IP address selection in
Section~\ref{sec:addr-selection}.

Once the phantom host IP address has been selected, the station watches for
packets destined to that address, and forwards them onto the phantom host
\textbf{application}. The station only forwards packets that originate from the
IP address of the registering client, making the phantom host appear as
firewalled off to everyone but the client.
We note that censors have been observed taking over client IP
addresses for follow-up probing~\cite{ensafi-tor}, which would allow censors to
still communicate with registered phantom hosts despite this filter.
However, filtering in this way does prevent censors from enumerating the
address space before hand, as they would have to do so from every potential
client IP address. Simply scanning the prefixes with ZMap~\cite{zmap13} from a
single vantage point would not reveal hosts that only respond to specific IPs
(e.g. are firewalled off).
%We instead address active probing in the application.

\subsection{Applications}

Once the client has registered, packets sent to the phantom host IP address are
passed to the \textbf{application} running on the station, which provides
proxy access to the client. The application has
two main requirements: first, the protocol it uses with the client 
must be difficult for the censor to \emph{passively detect} and block by traffic
inspection. Second, the application must resist \emph{active probes} by the censor (who
does not know the registration seed).

Any protocol that satisfies these criteria can be used as an application. In
this section, we describe existing protocols (obfs4 and obfuscated SSH) as well
as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
can be used in \scheme, and evaluate how each meet the necessary requirements.
Figure~\ref{fig:overview} describes a high-level overview of the \scheme
registration and application behavior, and Table~\ref{tab:applications} compares the
application protocols.

@@

\texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
Tor~\cite{tor} designed to resist both passive detection and active probing.
Traffic is obfuscated by encrypting it and sending headerless ciphertext
messages, and clients can only connect to \texttt{obfs4}
servers by proving knowledge of a secret. Probing censors that do not have the
secret get no response from \texttt{obfs4} servers, making it difficult for
censors to confirm if a host is a proxy. Server IPs and their corresponding secrets
are normally distributed out-of-band through Tor's bridge distribution system.

We can adopt \texttt{obfs4} for use as a \scheme application, with minimal
modification. During
registration, the \scheme client and station can use the registration seed to
derive the \texttt{obfs4} secrets (NODE\_ID and server private/public keys)
needed for the client to connect. The station then launches an \texttt{obfs4} server
instance at the registered phantom address, and the client can connect to it using the
derived secrets. If a censor attempts to connect to the phantom address (even
using the client's IP), it will not receive a response, as it does not know the
registration seed used to derive the \texttt{obfs4} secrets.

@@

%However, even though \texttt{obfs4} is indistinguishable from random, there are
%still known attacks that can differentiate it from other
%traffic~\cite{wang2015seeing}. While we have yet to see evidence of such attacks
%employed in practice by censors, we consider two alternatives built on TLS.

%Besides obfs4, we next describe in detail several alternative application
%protocols based on SSH, TLS, and WebRTC. These
%alternatives neatly demonstrate the flexibility of \scheme in allowing deployments
%to support multiple application protocols. Should censors develop ways to
%identify and block one protocol, others can still be used to provide proxy
%access.

Obfuscated SSH~\cite{ossh} (OSSH) is a protocol that attempts to mask the Secure Shell
(SSH) protocol in a thin
layer of encryption. This makes it difficult for censors to identify using basic
packet filters, as there are no identifying headers or fields
to search for. Instead, Obfuscated SSH clients first send a 16-byte random seed, which
is used to derive a symmetric key that encrypts the rest of the
communication. Early versions of OSSH were passively detectable by censors, who
can observe the random seed and derive the key, allowing them to de-obfuscate the protocol.
These versions also did
not protect against active probing attacks, as a censor can easily create their
own connections to confirm if a server supports the protocol.

%While this can passively detected by censors (who can also
%derive the key and de-obfuscate the protocol), the key derivation is deliberately
%slowed by an iterated hash to make such identification
%expensive (though not impossible) at high speeds.
%
%
%% This is wrong...it actually does protect against active probing
%Obfuscated SSH also does not protect against active probing, as the censor can
%easily create their own connections and confirm the server is using the
%protocol. Nonetheless, this protocol is still used in deployed censorship
%circumvention systems~\cite{psiphon}, though has to deploy proxies at new IP
%addresses when censors inevitably discover and block them.
%Obfuscated SSH can also be used as a \scheme
%application protocol, though we note it provides no active probing or passive
%identification resistance. However, \scheme OSSH can still make it cheaper to
%rotate to new IP addresses when proxies are found and blocked.

\subsubsection{Mask Sites}
\label{sec:mask-sites}

@@

One challenge is that TLS sends important server-identifying content in plaintext
during the TLS handshake. This includes the Server Name Indication (SNI) in the
Client Hello message that sends the domain name of the server, and the
X.509 Certificate sent by the server.

@@

We therefore attempt to mimic an existing \textbf{mask site} by relaying
traffic between the client and a selected mask website. To a censor, this site
will be indistinguishable from the actual site, making it difficult for
them to block without potentially blocking the real site. TLS connections to the
application will terminate exactly as connections to the mask site would, with the
application acting as a transparent TCP-layer proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-site shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

To covertly signal to the relaying application, the client changes the shared secret
it derives with the
mask site to something that the application can also derive. The client's first
\texttt{Application Data} packet is thus encrypted under a different secret than
the client/mask site secret. Specifically, the client uses the \textbf{seed}
sent during registration to derive the pre-master secret for the connection.
The new pre-master secret is hashed along with the client and server randoms of the current
(mask site) TLS connection to obtain the master secret that determines
encryption/decryption/authentication keys.

The application can determine if the client did this by trial decryption with
the master secret derived from the known \textbf{seed}. If it succeeds, the
client has proved knowledge of the \textbf{seed}, and the application can
respond as a proxy. If not, the application simply continues to forward data
between the client and the mask site. As the censor does not have knowledge of
the \textbf{seed} used in registration, it cannot coerce the application to
appear as anything besides the mask site.

\subsubsection{Mask Site Selection}

Selecting which sites to masquerade as must be done carefully to avoid censors
being able to detect obvious choices. For example, if a small university network
has a phantom host in their network that appears to be \texttt{apple.com}, it
would be easy for a censor to block as a likely non-legitimate host. Likewise,
if a phantom host at an IP address pretends to be a domain (\texttt{example.com}) that
globally resolves to a single different IP address, the censor could also
identify and block the phantom host.

\paragraph{Nearby sites.}
One strategy for selecting mask sites to mimic is to pick websites that are
legitimately hosted in or near the network of the phantom host addresses. This
effectively creates copies of legitimate sites, with the censor unable to
determine which copies are real and which are the phantom hosts. However, as
mentioned, other signals such as DNS may reveal the true mask site.

\paragraph{Popular sites.}
An alternative strategy is to use popular sites, such as those from the Alexa
top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
sites that are obviously not hosted in the phantom host address range, such as
large companies that run their own data centers and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a phantom host corresponds to a domain's IP.

\paragraph{Passive observation.}
The ISP tap could also collect sites by passively observing DNS requests, TLS
SNI, or certificates that pass by. This would allow for building a realistic set
of sites that are plausibly in the vicinity of the phantom host addresses
that pass by the tap. It also has the added bonus of being able to discover
IPv6 addresses that could be used as decoys (for registration), where active
scanning would be infeasible.

In practice, clients can often try phantom hosts/mask sites over
several attempts, as blocking the client outright may negatively impact other
unrelated users behind the same network (e.g. in the case of NAT). Thus, even a
censor that can block most (but not all) mask site only delays access, and
doesn't prevent it outright.

\subsubsection{Encrypted SNI}
\label{esni}

TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
\scheme application design. For instance, TLS~1.3 handshakes include encrypted
certificates, potentially obviating the need to impersonate mask sites.
Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
Hello, meaning we would still have to choose a realistic domain to fool a
censor.

However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
though none have been implemented or deployed as of 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
\scheme applications by allowing the domain to remain hidden from the censor.
While the censor could still try to actively probe with guesses for the SNI,
servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify phantom hosts
would be frustrated.

@@

Phantom hosts could also pretend to be clients instead of servers. This may
potentially give censors less to block on, as actively probing clients is common
to return few or no open ports. Nonetheless, a censor may be hesitant to block
client-to-client communication, as it could block peer-to-peer applications as
well as many video conferencing protocols. WebRTC is a
natural choice for a client-to-client protocol in censorship circumvention,
and is used in existing censorship circumvention schemes like
Snowflake~\cite{snowflake}. \scheme could also use WebRTC as the
application protocol, convincing the censor that two clients are communicating.

@@

Phantom host IP addresses must be derived from network blocks that are routed (so they pass
the ISP station) and contain other legitimate hosts (so that censors cannot
block the entire network without collateral damage).
Because of the large number of IPv6 addresses, even
moderately-sized network prefixes have astronomical numbers of addresses: a
single /32 prefix has $2^{96}$ possible addresses. Therefore, client-chosen
seeds have negligible probability of corresponding to addresses that are already
being used by legitimate hosts. This allows us to select phantom host addresses
from network prefixes that contain
legitimate hosts---crucial to discouraging the censor from blocking them
outright---without worry that registrations could interfere with legitimate
services.

%We emphasize that TapDance is already
%vulnerable to active probing attacks~\cite{tapdance14} that \scheme defends
%against when using IPv6. However, in IPv4, there are substantially fewer
%addresses, allowing censors to easily enumerate network prefixes that pass by
%the ISP station and measure legitimate sites. Furthermore, the small address
%space makes it much easier to pre-image the hash used to derive IP addresses
%from the seed. Registering a specific IPv4 address in an IPv4 /16 subnet will
%take only an expected $2^{16}$ hashes for the censor to achieve. This would let
%attackers register legitimate hosts as phantom hosts, potentially disrupting
%legitimate service. If the station refused to pick up for addresses that
%correspond to legitimate hosts (measured by scanning during registration), then
%censors could use this as an oracle for distinguishing legitimate sites from
%phantom hosts. Still, IPv4 \scheme offers many performance, flexibility, and
%simplicity benefits over TapDance, though they are both vulnerable to active
%probing attacks.

@@

We implemented the \scheme protocol and deployed a station at a
20~Gbps router in a mid-sized transit ISP. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
consume the 20~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) phantom host address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

@@

%Compare to TapDance performance:
%-Connection setup time
%-Connection/session lifetime
%-Throughput (especially upload vs download)
%-Security considerations

%\section{Discussion}

@@

\paragraph{Client-side applications}
On the application side, \scheme provides an interesting opportunity to explore
\emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.,
a mask site), our application could connect back to a client after registration
from the phantom host address. Possible protocols could include WebRTC, mentioned in
Section~\ref{sec:webrtc}, or other peer-to-peer protocols such as BitTorrent,
Skype, or Bitcoin.

>>>>

%\TODO{more precise:}
In our scheme (Figure~\ref{fig:highlevel}), clients
register their intentions to connect to phantom hosts in the ``dark''
or unused address space of the deploying ISP. Once registered, clients
can connect to these phantom hosts IP addresses as if they were real
proxy servers. The \scheme station (deployed at an ISP) acts as the other end of these connections, and
responds as if it were a legitimate site or service. To the censor,
these phantom hosts appear as legitimate sites or services, and even
active probes will not reveal information that would allow the censor to
block them.

%% requests service
%% by embedding a steganographic registration message in a TLS handshake
%% with a decoy site. This message, which the \scheme station can passively
%% observe using a private key, uniquely determines an IP address within
%% the ISP's address space. If there is no server running at that address,

@@

\TODO{Phantom hosts are cheap to create, allowing for discardable or even one-time-use
proxy servers}. This greatly increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
can detect 90\% of phantom hosts does not significantly increase the cost to the
circumvention system, giving \scheme an advantage in the censor/circumventor
cat-and-mouse game.
%TODO: don't need to hedge on IPv4 anymore..? could cut
\scheme supports both IPv4 and IPv6,
though we note that the technique is especially
powerful in IPv6, where censors cannot exhaustively scan the address space
ahead of time to identify addresses that change behavior.
Because we fully control the transport connection, connections can live as
long as needed, without the complexity faced by TapDance.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented \scheme (Section~\ref{sec:implementation})
and deployed it on a 20~Gbps ISP testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}): on average, \scheme has 20\% lower latency,
14\% faster download bandwidth, and over 1400 times faster upload bandwidth.
In addition, \scheme provides significantly
more flexibility than existing Refraction protocols, allowing maintainers to
respond to future censor techniques.
We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

@@

\scheme involves two high-level steps. First, clients \textbf{register} with a 
\scheme station deployed at an ISP, and derive a phantom host IP address from 
a seed shared in the registration. Then, clients \textbf{connect} 
to the agreed upon phantom address, and the station listening on the tap 
relays the client's traffic to a local application. The application brokers 
traffic to a proxy application specified by the client in their registration 
providing a probe resistant tunnel. Figure~\ref{fig:overview} describes a 
high-level overview of the \scheme registration and connection behavior.

Similar to previous schemes, our design does not require expensive in-line
flow blocking and is accomplished with only a passive tap at the ISP, imparting
little to no burden on their infrastructure and service reliability.
Our architecture is also modular, in that the registration and connection steps operate
independently, allowing a wide range of flexibility to evade censors. We
describe each of these components, and then describe our implementation and
deployment in Section~\ref{sec:implementation}.

\subsection{Registration}
\label{sec:registration}
We use a form of refraction networking similar to Tapdance to register directly with
the station, though \scheme registration is significantly simpler and more difficult
to detect than vanilla Tapdance. This is because registration flows are unidirectional; 
a client communicates their intent to register to the station without any 
response from the station itself. This makes registration flows very difficult to detect as they 
can be sent to any site hosted behind the ISP, and display no evidence of proxy behavior.

While this model of registration gives the client no definitive indication that their 
registration was successful, the client can attempt to register
multiple times concurrently with the same information, 
and expect that one gets through. Alternatively clients can register intent to use the 
proxy in other covert ways. For instance, they could use email~\cite{SWEET-ToN} or any 
other existing intermittently available proxies to register.

@@

A registration connection is sent to a \textbf{registration decoy}: any site that 
supports TLS behind the ISP relative to the client. The client completes the handshake,
and sends a normal HTTPS request that embeds a ciphertext tag in the payload. 
\scheme leverages the same steganographic technique as Tapdance to encode the 
ciphertext~\cite[\S3]{tapdance14}, however we send a complete request allowing the
registration decoy to respond or close the connection. The tag is encrypted such 
that it is only visible to the station. The \scheme station passively observes
tagged flows obviating the need to mimic the decoy. In addition, more potential 
decoys can be used in comparison to TapDance, as there is no need to exclude decoys that 
have timeouts or TCP windows unfavorable for keeping connections open. In our 
deployment, this results in a modest increase of 25\% more decoys that could be 
used than in TapDance.

The tag contains a public key (encoded to be indistinguishable from random using
Elligator~\cite{elligator}), and a message encrypted under the shared secret
derived from a Diffie-Hellman key exchange with the station's long-term public key hard-coded
in the client. The station uses its private key to compute the same
shared secret from the (decoded) client public key, and decrypts the message in the
tag. The censor, without knowledge of either the station or client's private
key, cannot derive the shared secret, preventing it from being able to decrypt
the message, or even learn of its existence.

Inside the message, the client communicates a random seed, the covert address 
they would like to connect to, the transport protocol they will use, and other
configuration-specific information, such as flags to signify version, and feature support.
The client and server hash the seed to determine which specific
IP address from the set of shared CIDR prefixes will be used and registered as a phantom host.
It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected phantom hosts and block them if
they can be used as proxies.
By using a hash of a seed, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address.
We discuss the intricacies of phantom IP address selection in
Section~\ref{sec:addr-selection}.

Once the phantom host IP address has been selected, the station watches for
packets with the source address of the original client and the phantom as the destination, 
and forwards them on to the a local application handling transports. The station only 
forwards packets that originate from the IP address of the registering client, making the
 phantom host appear firewalled off to everyone but the client.
We note that censors have been observed taking over client IP
addresses for follow-up probing~\cite{ensafi-tor}. This would allow censors to
hijack registrations if they can connect within the small window between client 
registration and connection. However this only 
allows the censor to communicate to the local application that handles transports, 
it does not connect them to the covert address that the client indicated in their registration. 
Filtering by client IP and phantom IP also prevents censors from enumerating the
address space before hand, as they would have to do so from every potential
client IP address. Simply scanning the prefixes with ZMap~\cite{zmap13} from a
single vantage point would not reveal hosts that only respond to specific IPs
(e.g. firewalled subnets).

\subsection{Transports}

Once the client has registered, packets sent to the phantom host IP address are
detected at the station and passed to the local \textbf{application} which provides
proxy access to the client. A viable \scheme transport has
two main requirements: first, the protocol it uses with the client 
must be difficult for the censor to \emph{passively detect} and block by traffic
inspection. Second, the endpoint must resist \emph{active probes} by the censor (who
does not know some shared secret).

Any protocol that satisfies these criteria can be used as an effective transport
with \scheme. In this section, we describe various existing protocols (OSSH and obfuscated Obfs4) as well
as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
can be used in \scheme, and evaluate how each meet the necessary requirements.
Table~\ref{tab:applications} compares the application protocols. \scheme uses a modular 
approach to transports because research into proxy detection is ongoing.
Having a variety of supported transports gives clients a quick way to pivot and 
maintain proxy access even when new proxy protocol vulnerabilities are discovered.

Obfuscated SSH~\cite{ossh} (OSSH) is a protocol that attempts to mask the Secure Shell
(SSH) protocol in a thin
layer of encryption. This makes it difficult for censors to identify using basic
packet filters, as there are no identifying headers or fields
to search for. Instead, Obfuscated SSH clients first send a 16-byte random seed, which
is used to derive a symmetric key that encrypts the rest of the
communication. Early versions of OSSH were passively detectable by censors, who
could observe the random seed and derive the key, allowing them to de-obfuscate the protocol.
These versions also did
not protect against active probing attacks, as a censor could easily create their
own connections to confirm if a server supports the protocol.

% \TODO{We have implemented OSSH as a transport option by integrating with psiphon.}

@@

\texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
Tor~\cite{tor} designed to resist both passive detection and active probing.
Traffic is obfuscated by encrypting it and sending headerless ciphertext
messages. Similar to OSSH, clients can only connect to \texttt{obfs4}
servers by proving knowledge of a secret. Probing censors that do not have the
secret get no response from \texttt{obfs4} servers, making it difficult for
censors to confirm if a host is a proxy. Server IPs and their corresponding secrets
are normally distributed out-of-band through Tor's bridge distribution system.

During registration, the \scheme client and station could use the registration seed to
derive the \texttt{obfs4} secrets (NODE\_ID and server private/public keys)
needed for the client to connect. The station could then launch an \texttt{obfs4} server
instance locally for the client to connect to as a transport using the
derived secrets. If a censor attempts to connect to the phantom address (even
using the client's IP), it will not receive a response, as it does not know the
registration seed used to derive the \texttt{obfs4} secrets.

@@

\subsubsection{TLS}

@@

One challenge is that TLS sends important server-identifying content in plaintext
during the TLS handshake. This includes the Server Name Indication (SNI) in the
Client Hello message that specifies the domain name, and the
X.509 Certificate of the server.

@@

\paragraph{Encrypted SNI}
\label{esni}

TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
\scheme transport design. For instance, TLS~1.3 handshakes include encrypted
certificates, removing a strong traffic classification feature.
Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
Hello, meaning we would have to choose a realistic domain to fool a censor.

However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
though none have been implemented or deployed as of 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
\scheme applications by allowing the client to use plain TLS as the transport
while remaining hidden from the censor.
Censors could still try to actively probe with guesses for the SNI,
servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify phantom hosts
would be frustrated.

\paragraph{Mask Sites}
\label{sec:mask-sites}

Working with currently popular implementations of TLS we overcome the active 
and passive probing challenges by mimicking an existing mask site. To a censor, this site
will be difficult to distinguish from the actual site, making it expensive for
them to block without potentially blocking the real site. TLS connections to the
\scheme station will terminate exactly as connections to the mask site would, with
\scheme acting as a transparent TCP-layer proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-side shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

To covertly signal to the relaying application, the client changes the shared secret
it derives with the mask site to something that the \scheme station can also derive. The client's first
\texttt{Application Data} packet is thus encrypted under a different secret than
the client/mask site secret. Specifically, the client uses the \textbf{seed}
sent during registration to derive the pre-master secret for the connection.
The new pre-master secret is hashed along with the client and server randoms of the current
(mask site) TLS connection to obtain the master secret that determines
encryption/decryption/authentication keys.

The \scheme station can determine if the client did this by trial decryption with
the master secret derived from the known seed shared at registration. If it succeeds, the
client has proved knowledge of the seed, and the application can
respond as a proxy. If not, the application simply continues to forward data
between the client and the mask site, in case a clients IP was taken over by
a censor after registration. As the censor does not have knowledge of
the \textbf{seed} used in registration, it cannot coerce the application to
appear as anything besides the mask site.

\paragraph{Mask Site Selection}

Selecting which sites to masquerade as must be done carefully to avoid censors
being able to detect obvious choices. For example, if a small university network
has a phantom host in their network that appears to be \texttt{apple.com}, it
would be easy for a censor to block as a likely non-legitimate host. Likewise,
if a phantom host at an IP address pretends to be a domain (\texttt{example.com}) that
globally resolves to a single IP address, the censor could also trivially
identify and block the phantom host.

\textit{Nearby sites --} pick websites that are
legitimately hosted in or near the network of the phantom host addresses
effectively creating copies of legitimate sites. However, other signals such as 
DNS may reveal the true mask site.

\textit{Popular sites --} choose mask sites from a list such as the Alexa
top site~\cite{alexa-top500} list. Although it may be wise to avoid
sites that are obviously not hosted in the phantom host address range, such as
large companies that run their own data centers and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a phantom host corresponds to a domain's IP.

\textit{Passive observation --} collect sites by passively observing DNS requests, TLS
SNI, or certificates that pass by at the network tap. This would allow for building a realistic set
of sites that are plausibly in the vicinity of the phantom host addresses
that pass by the tap.

In practice, clients can often try multiple phantom hosts/mask sites over
several attempts, as blocking the client outright may negatively impact other
unrelated users behind the same network (e.g. in the case of NAT). Thus, even a
censor that can block most but not all mask site usage (i.e. by employing 
website fingerprinting) only delays access, and doesn't prevent it outright.

@@

Phantom hosts could also pretend to be clients instead of servers. This may
potentially give censors less to block on, as actively probing clients commonly
returns few or no open ports. A censor may also be hesitant to block
client-to-client communication, as it could block peer-to-peer applications as
well as many video conferencing protocols. WebRTC is a
natural choice for a client-to-client transport in censorship circumvention,
and is already used in existing schemes like
Snowflake~\cite{snowflake}. \scheme could also use WebRTC as the
transport protocol, convincing the censor that two clients are communicating.

@@

@@

We implemented the \scheme protocol and deployed a station at a
20~Gbps router in a mid-sized transit ISP. We used PF\_RING to
consume the 20~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) phantom host address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

@@

Phantom host IP addresses must be derived from network blocks that are routed (so they pass
the \scheme station) and contain other legitimate hosts (so that censors cannot
block the entire network without collateral damage).
Because of the large number of IPv6 addresses, even
moderately-sized network prefixes have astronomical numbers of addresses: a
single /32 prefix has $2^{96}$ possible addresses. Therefore, client-chosen
seeds have negligible probability of corresponding to addresses that are already
being used by legitimate hosts. This allows us to select phantom host addresses
from network prefixes that contain
legitimate hosts---crucial to discouraging the censor from blocking them
outright---without worry that registrations could interfere with legitimate
services.

%We emphasize that TapDance is already
%vulnerable to active probing attacks~\cite{tapdance14} that \scheme defends
%against when using IPv6. However, in IPv4, there are substantially fewer
%addresses, allowing censors to easily enumerate network prefixes that pass by
%the \scheme station and measure legitimate sites. Furthermore, the small address
%space makes it much easier to pre-image the hash used to derive IP addresses
%from the seed. Registering a specific IPv4 address in an IPv4 /16 subnet will
%take only an expected $2^{16}$ hashes for the censor to achieve. This would let
%attackers register legitimate hosts as phantom hosts, potentially disrupting
%legitimate service. If the station refused to pick up for addresses that
%correspond to legitimate hosts (measured by scanning during registration), then
%censors could use this as an oracle for distinguishing legitimate sites from
%phantom hosts. Still, IPv4 \scheme offers many performance, flexibility, and
%simplicity benefits over TapDance, though they are both vulnerable to active
%probing attacks.

@@

\paragraph{Client-side applications}
\TODO{On the application side}, \scheme provides an interesting opportunity to explore
\emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.,
a mask site), our application could connect back to a client after registration
from the phantom host address. Possible protocols could include WebRTC, mentioned in
Section~\ref{sec:webrtc}, or other peer-to-peer protocols such as BitTorrent,
Skype, or Bitcoin.
